---
title: "CS 422 - Homework 8"
author: "Imaduddin Sheikh"
output:
  html_document:
    toc: yes
    df_print: paged
  pdf_document:
    toc: yes
  html_notebook:
    toc: yes
    toc_float: yes
---

###### Due Date: Tuesday, April 19 2022 11:59:59 PM Chicago Time

******

### 2. Practicum Problems

******

### 2.1. K-means clustering

******

```{r}
library("factoextra")
library("ggplot2")
library("dplyr")
library("cluster")
setwd("~/Homework 8")
```

```{r}
txt.to.df <- function(txt.file,out.df) {
  file19.txt.df <- read.csv(file= txt.file,
                           header = FALSE,
                           sep = "",
                           dec = ".",
                           comment.char = "#"
                           
                           )
  
  write.csv(file19.txt.df, file = out.df)
  file19.txt.df <- read.csv(file= out.df,
                           header = TRUE,
                           sep = ",",
                           dec = ".",
                           comment.char = "#",
                         skip = 4
                           )
  write.csv(file19.txt.df[,1:10], file = out.df,row.names = F)
  file19.txt.df <- read.csv(out.df,row.names = 1)
  row.names(file19.txt.df) <- NULL
  
  return( file19.txt.df)
}
```

******

### Part 2.1(a)

******

```{r}
file19.df <- txt.to.df(txt.file = "file19.txt", out.df = "file19.csv")
dim(file19.df)
```
******

```{r}
file19.df
```

```{r}
summary(file19.df)
```

```{r}
apply(file19.df,2,sd)
```

******

### Part 2.1(a)(i)

******

<span style="color: blue;">Only the names <b>Name</b> feature is to be omitted. For the remaining features, the summary of the data extracted from the <i>file19.txt</i> and the standard deviations of the features indicate that they do not need to be omitted.</span>

******

```{r}
df <- file19.df[-1]
df
```

******

### Part 2.1(a)(ii)

******

<span style="color: blue;">The mean of the data is not equal to zero for each feature. Hence, the data is not standardized.</span>

******

```{r}
scaled.df <- scale(df)
```

```{r}
summary(scaled.df)
```

******

### Part 2.1(a)(iii)

******

<span style="color: blue;">The function implemented created at the start of the R notebook takes care of the cleaning and the creation of the cleaned data set. The function is called <i><b>txt.to.df</b></i>, and the cleaned data set is titled <i><b>file19.csv</b></i>.</span>

******

### Part 2.1(b)

******

### Part 2.1(b)(i)

******

```{r}
fviz_nbclust(scaled.df, kmeans, method="silhouette")
```

```{r}
fviz_nbclust(scaled.df, kmeans, method="wss")
```

******

<span style="color: blue;">After taking both the WSS and Silhouette graphs into account, I feel that the 8 would be an ideal number for clusters. The average silhouette value is highest and the total WSS the second-lowest(very close to the minimum) when k = 8.</span>

******

### Part 2.1(b)(ii)

******

```{r}
k <- kmeans(scaled.df, centers=8, nstart=25)
```

******

```{r}
k
```

```{r}
fviz_cluster(k, data=scaled.df)
```

******

### Part 2.1(b)(iii)

******
 
```{r}
ob.per.cluster <-as.data.frame(table(k$cluster))
names(ob.per.cluster) <-c("Cluster","Observations")
print(ob.per.cluster)
```

******

### Part 2.1(b)(iv)

******
 
```{r}
print(paste("Total SSE of the clusters is", signif(k$tot.withinss, 5),"."))
```

******

### Part 2.1(b)(v)

******

```{r}
sse.cluster <-c()
for (x in 1:max(k$cluster)){
  sse.cluster <-rbind(sse.cluster,c(x,k$withinss[x]))
}
colnames(sse.cluster) <- c("Cluster", "SSE")
print(sse.cluster)
```

******

### Part 2.1(b)(vi)

******

```{r}
for (i in 1:8) {
  print(paste0("Group ", i, ": ", paste(unlist(file19.df[which(k$cluster==i),][1], use.names=FALSE), collapse=", ")))
}
```

******

<span style="color: blue;">I believe that all the results meet my expectations. I expected that members of the animal kingdom like bats, squirrels, and rats are all clustered together in their own groups. Secondly, Group 4 contains animals that mostly make up livestock, if not entirely. The Other 7 groups include animals are either from entirely different classes, or similar classes. I don't believe animals of similar/same class will be found in another group/cluster, unless the features significantly set them apart. In terms of SSE's, the <b>Total SSE</b> is ~52.3, so it is not bad. The ratio <b>between_SS / total_SS</b> is close to 90% which is a pretty good number. Lastly, looking at the <b>within SSE</b> metric for each cluster indicates a good clustering performance overall.<span>

******